%-------------------------
% Cover Letter in Latex
% Matching the CV format
%-------------------------

\documentclass[11pt,a4paper]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}

% ATS-friendly settings
\input{glyphtounicode}
\pdfgentounicode=1

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\begin{document}

\begin{center}
    {\Huge \scshape Anil Celik Maral, Cover Letter} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +49 152 24885420 ~ \href{mailto:anilcelikmaral@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{anilcelikmaral@gmail.com}} ~ 
    \href{https://anilcelikmaral.com/}{\raisebox{-0.2\height}\faGlobe\ \underline{anilcelikmaral.com}}  ~
    \href{https://www.linkedin.com/in/anil-celik-maral/}{\raisebox{-0.2\height}\faLinkedin\ \underline{anil-celik-maral}}  ~
    \href{https://github.com/Popichi}{\raisebox{-0.2\height}\faGithub\ \underline{Popichi}}
\end{center}

\vspace{10pt}

\begin{flushleft}
\textbf{\today}
\end{flushleft}

\begin{flushleft}
Hiring Manager\\
CARIAD\\
\end{flushleft}

\vspace{-15pt}

\begin{flushleft}
Dear Hiring Manager,
\end{flushleft}

\begin{flushleft}

I am writing to express my enthusiasm for the intern/working student position 
within the "Architecture \& Technologies" team at CARIAD, as advertised. With 
a strong foundation in computer sciences, bolstered by hands-on experience in 
C/C++, Python, Matlab \& Simulink, I am excited about the opportunity to 
contribute to the development and transformation of digital mobility within 
the Volkswagen Group.
    
\end{flushleft}

\begin{flushleft}
My academic background and project work have equipped me with a solid 
understanding of the skills required for the advertised job. I am particularly 
drawn to the role’s focus on enhancing vehicle diagnostics and over-the-air 
updates.
\end{flushleft}

\begin{flushleft}
I am fluent in both English and conversational in German, which, combined with 
my technical skills and a keen interest in automotive technologies, positions 
me well to collaborate effectively with your team and across brands. The 
chance to work on the E/E and software architecture for prestigious brands
like Volkswagen, Audi, and Porsche is a challenge I am eager to embrace.
\end{flushleft}

\begin{flushleft}
Thank you for considering my application. I am looking forward to the 
opportunity to discuss how my background, skills, and enthusiasms align 
with the goals of CARIAD. I am eager to contribute to your team's success 
and the advancement of innovative automotive technologies.
\end{flushleft}

\begin{flushleft}
Sincerely,
\end{flushleft}

\begin{flushleft}
Anil Celik Maral
\end{flushleft}

\end{document}
